Frozen Civil Conflicts

### 2024-02-20 paper.qmd
Draft edits

Frozen conflicts are among some of the most pernicious, difficult to
resolve conflicts. Surprisingly, little scholarly attention has been
paid to the factors influencing their emergence. This paper addresses

Frozen conflicts -> pernicious difficult to solve conflicts; long-running costs

>>>>

Frozen conflicts are among some of the most pernicious, difficult to
resolve conflicts. When conflicts freeze large-scale hostilities cease, but the underlying issue(s) remain unresolved with an ever present threat of recurrent violence. This state of unstable peace can be costly for actors as a certain degree of military preparedness needs to be maintained to secure transitory war gains lest the conflict reignites leading to an outright military defeat.

Suprisingly, little scholarly attention has been paid to the factors influencing the emergence of frozen conflicts. Previous empirical work tends to consist of qualitative single-case studies [@klosek_frozen_2021].

Surprisingly, little scholarly attention has been
paid to the factors influencing their emergence. This paper addresses
